Using Random Walk Simulations to Calculate Ground State Energies in Quantum Physics

### 2020-04-20 Paper/main.tex
Made many minor changes based on feedback

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
  In this paper, we present a novel way of calculating ground state energies for
  a quantum simulation using a Random Walk Monte Carlo simulation. The random
  walk consists of a walker making steps in random directions, with each step
  having a probability of causing the walker to die and the random walk to end,
  with the probability determined by a function of position. The function can be
  chosen to model specific quantum systems. The rate of death of the walkers is
  used to calculate the ground state energy.

  This paper explores the efficacy of such a method in reproducing the known
  ground state energy of an infinite square well, and the extensibility of the
  method to more complex systems. We found that this method is very good at
  reproducing the known results to a high precision, and with good reliability,
  having very small variance in repeats. The method is extensible to higher
  dimensions, with a linear increase in time-complexity for each added dimension.
\end{abstract}

\section{Introduction}
\IEEEPARstart{T}{he} developments in computer power in recent years has opened
up the possibility for novel computational solutions to many problems that were
otherwise limited. We now have access to computers that can numerically solve
problems and run simulations that were previously too computationally intensive
to do.

One such problem is the calculation of the ground state energies of different
quantum systems. Many methods exist for solving these problems, using both
classical and quantum computational approaches. Whilst generally it may be true
that Quantum computating approahes are more suited to solving such problems
\cite{Mazzola}, these approaches are still in infancy and are not readily
accessible. Thus, there exist an abundance of classical computing approaches,
such as the Variational-Relaxiation algorithm \cite{Schroeder2017}. This is a
particularly useful algorithm for two-dimensional systems with non-separable
potentials but quickly becomes difficult to implement for more complex systems.

In this investigation, we explore an alternative Monte Carlo method using Random
Walk simulations, and demonstrate its efficacy with simple systems.

@@

Random walks descibe motion as a series of steps in some vector space, with the
direction of each step being random, i.e. with there being an equal likelihood
of a step in each possible direction. Consider a simple 1-dimensional line and a
walker standing at a point labelled the origin. The walker takes 20 steps, the
direction of each step (forwards or backwards on the line) is random. The
position of the walker at each step is shown in Figure \ref{fig:cartoon}.

\begin{figure}[H]%[!ht]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{images/cartoon.pdf}
    \caption{The position of a walker at each step in a 20-step random walk
      simulation. The average position of the walker does not necessarily remain
      at the origin as one might naively expect. Instead it is normal for the
      walker to finish the walk at some distance from the origin, as shown here.}
    \label{fig:cartoon}
  \end{center}
\end{figure}

@@

In this example, the walker had an equal likelihood of stepping forward or
backwards, but we can bias in one way if we want to model a particular
phenomenon. The walk is also easily extensible to multiple dimensions, as for
each extra dimension, one extra random number must be drawn. This gives a linear
increase in time-complexity, which is convenient for more complex systems.

@@

Let us define $p(j,n)$ as the probability that the walker will be at position
$j$ after $n$ steps and $a(j)$ as the probability that the walker will die at
position $j$. Thus, for this to be the case, the walker would have had position
$j\pm1$ after $n-1$ steps. Thus, we can say:

@@

If $a(j)$ is small and $n$ is large, we can use Taylor's expansion to expand
each term in this expression and obtain a differential equation. If we then
make the ansatz substitution:

\begin{equation}
  p(j,n) = q(j) \exp(-\lambda n)
  \label{eq:firsteq}
\end{equation}
where $q(j)$ is an arbitrary function and $\lambda$ is the rate of death, then
we find:

@@

\begin{equation}
  \label{eq:squarewell}
    a(j) =
    \begin{cases}
      0,& \text{if } j < J\\
      \infty,& \text{if } j \geq J
    \end{cases}
    \nonumber
\end{equation}
where J is a well-defined boundary. So the walker cannot die inside the well but
wil immediately die when they step outside, which we expect will definitely
happen given sufficient time. Inside the well, the potential is simply that of a
free particle \cite{Bransden2003}:

\begin{equation}
  \frac{-\hbar^2}{2m}\frac{d^2 \psi}{dx^2} = E\psi(x)
  \nonumber
\end{equation}
where $x$ is the position of the walker. By making the substitution
$x=J\frac{j}{R}$, such that $j=R$ corresponds to the walker being at the
boundary, we find:

@@

\begin{equation}
  E = \lambda R^2 \frac{\hbar^2}{mJ^2}
  \nonumber
\end{equation}
where only $\lambda$ is an unknown quantity. Thus, by calculating rate of death
$\lambda$, we can calculate the ground state energy of the infinite square
well. The known ground state energy of an infnite square well is
$\frac{\pi^2}{8}\frac{\hbar^2}{mJ^2}$ \cite{Davies1998}, so we expect to find $\lambda
R^2$ close to $\frac{\pi}{8}$.

@@

We then consider the probability that a walker will survive $n$ steps, and use
the relationship between the number of walkers surviving $n$ steps and $n$ to
determine the rate of death $\lambda$, as shown in Equation \ref{eq:straightline}.

One method of reducing the computing time of the simulation is to introduce a
maximum number of steps. The walker will die if they reach the boundary of the
well, or if they reach this maximum number of steps, whichever happens
first. However, this will introduce some systematic error into the simulation,
as there will be a disproportionately high number of walkers dying on the
maximum number of steps. We also investigated these effects here.

We expect to see an effect on the accuracy of our final ground state depending
on the size of the infinite well. We investigate these effects by comparing the
calculated ground state energy to the theoretical energy for different sized wells.

@@

\begin{figure*}[ht!]
  \centering
  \subfloat[Histogram of probability of surviving to at least a particlar step]
  {\includegraphics[width=0.5\textwidth]{images/cum_exp_plot.pdf}
  \label{fig:cumhist}}
  \centering
  \subfloat[Histogram of probability of surviving to at least a particular step
  in a logarithmic scale]
  {\includegraphics[width=0.5\textwidth]{images/cum_line_plot.pdf}
  \label{fig:cumloghist}}
  \caption{Histogram showing the Probability of surviving to at least a
    particular step in an infinite square well with $J = 20$. The peak of 1 does
    not start at the origin but at step 100. This is because these steps were
    neglected in the plot as prior to this step the exponential shape is less
    clear, as explained by Figure \ref{fig:hist}. An exponential decay curve
    provides a good fit, with an $R^2$ value of 0.9999998, very close to
    1. Plotting on a logarithmic scale shows the straight line fit, the gradient
    of which is $\lambda$, giving $\lambda J^2 = 1.2334$, with a negligible
    error. The fluctuation in the higher step number regions is due to the large
    variance in the small number of walkers that die at these steps.}
  \label{fig:cumplots}
\end{figure*}

The simulation was first run for an infinite square well with boundary $J=20$
with 1000000 walkers. The number of walkers surviving at each step was recorded
and the histograms in Figure \ref{fig:cumplots} were created. The probability
that a walker will survive at a particular step is simply the 1 minus the
normalised cumulative sum of walkers dying at each step. The curve has been
fitted with an exponential function of the form in Equation
\ref{eq:firsteq}. This results in a very good fit, with an $R^2$ value of
0.9999998, indicating the data does not vary much from the curve of best
fit. This is likely due to the very large number of walkers used in this
experiment, as allowed by the performant C++ implementation.

We can see this better in Figure \ref{fig:cumloghist}, which is the same
exponential plot fitted on a logarithmic scale. The closeness of the data to the
line of best fit is evident here. The error in the fitted parameters is
negligible, as shown by the $R^2$ value. The gradient of the fitted line is
taken to be $\lambda$ and thus allows us to calculate $\lambda J^2 = 1.2334$,
compared to the theoretical value of $\frac{\pi^2}{8} = 1.2337$, quoting both
values to the precision at which they vary. Since the numerical error in the
fits is negligible, it cannot be propagated into an error in the final
answer. Thus, we get the error in the final answer from repeated runs of the
simulation and taking the standard deviation of the many values.

@@

\begin{figure}%[!ht]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{images/line_plot.pdf}
    \caption{The probability of dying on a particular step in an infnite square
      well with $J=20$, plotted on a logarithmic scale. As explained for Figure
      \ref{fig:hist}, the peak probability is on a step greater than $J$. This
      is clear in this plot. It is also evident that there is significantly more
      spread in the points at higher steps. This is due to there being
      significantly fewer walkers dying on these steps, so the relative
      differences are higher. This explains the fluctuations seen at higher
      steps in Figure \ref{fig:cumloghist}.}
    \label{fig:loghist}
  \end{center}
\end{figure}

We observe some fluctuation in the data in the higher steps in Figure
\ref{fig:cumloghist}. This is because there are so few walkers surviving to this
many steps that there is more significant variance in their relative numbers. We
can observe this in Figure \ref{fig:loghist}. At higher step numbers, the spread
is clearly larger due to the greater relative variance in the small number of
walkers surviving to this many steps. When this data is cumulatively summed to
calculate the probability of survival shown in Figure \ref{fig:cumloghist}, the
spread is present as the fluctuations.

\begin{figure*}[ht!]
  \centering
  \subfloat[Probability of dying on a particlar step with a step cutoff]
  {\includegraphics[width=0.5\textwidth]{images/exp_plot_cutoff.pdf}
  \label{fig:expcutoff}}
  \centering
  \subfloat[Probability of surviving to at least a particular step in a
  logarithmic scale with a step cutoff]
  {\includegraphics[width=0.5\textwidth]{images/cum_line_plot_cutoff.pdf}
  \label{fig:cum_line_cutoff_plot}}
  \caption{Histograms showing the results of the simulation when a maximm number
  of steps is introduced. If a walker reaches this number of steps, they
  automatically die, regardless of position. This results in a
  disproportionately high number of walkers dying at this maximum number, 2000
  in this case, as shown by Figure \ref{fig:expcutoff}. However, this results in
  no fluctuation at higher number of steps, as shown in Figure
  \ref{fig:cum_line_cutoff_plot}, though some systematic error is introduced
  through this method.}
  \label{fig:cutoffplots}
\end{figure*}

It is possible to remove this variance by introducing a cutoff number of steps,
i.e. a maximum number of steps at which the walker will automatically die,
regardless of whether they reached a boundary or not. Thus, there will not be
such high variance in the number of walkers surviving to high number of
steps. This is presented in Figure \ref{fig:cum_line_cutoff_plot}. While this
fit is observed to be better, with a higher $R^2$ value, some systematic error
has been introduced since there will now be a disproportionately high number of
walkers dying at the cutoff step as can be seen in Figure
\ref{fig:expcutoff}. Thus, the final $\lambda J^2$ value will be less
accurate. On a faster computer, with more efficient code, it is possible to
forgo the step cutoff and allow the simulation to run until all the walkers
die. This may take much longer but will ensure there will not be such a
systematic error introduced. This is the method used in this investigation.

@@

It is also necessary to investigate how varying the boundary $J$ affects the
accuracy of the final answer. Figure \ref{fig:multi_line_plot} presents the
cumulative summed histograms with their fitted lines for many different boundary
$J$ values. No step cutoff was introduced. The calculated $\lambda J^2$ value is
shown in the legend. As shown, the gradient changes, but this is to be expected
since the expected highest number of steps would increase as the boundary is
larger, since there is more space for the walker to move before reaching a
boundary. As shown in the legend, the calculated $\lambda J^2$ values get closer
and closer and closer to the theoretical value as $J$ increases. This is due to
the fact that as $J$ increases, there are more walkers surviving to larger
number of steps. Thus, we can say that using a larger value of $J$ will result
in a more accurate answer but will also be more computationally intensive and
take longer. Thus, we make a tradeoff between speed and accuracy and choose
$J=20$ for the final investigation.

@@

In this investigation we demonstrated a method of calculating ground state
energies of a quantum system using Random walk computational simulations. The
investigation focussed on a one dimensional infinite square well, but can easily
be extended to more complex systems such as a circular well in two dimensions.

The investigation explored the effects of varying the size of the well in
determining the ground state energy of a quantum system, and showed that this
method produces more accurate results for ground state energies of larger wells.
This is because for wells with larger boundaries, the walker can take a larger
number of steps on average before dying, and thus can populate larger step
bins. Thus, this method produces data that is close to the theoretical result
for larger infinite square wells.

The general theoretical result for the ground state energy of an infinite square
well is $\frac{\pi^2}{8}\frac{\hbar^2}{mJ^2}$ where $J$ is the boundary of the
well, and this method allows for the calculation of $\lambda R^2
\frac{\hbar^2}{mJ^2}$, where $R$ also corresponds to the boundary of the
well. Thus, we expect our calculated result to be $\lambda J^2 =
\frac{\pi^2}{8}$.

This method provided $\lambda J^2 = 1.2339 \pm 0.0008$, which lies within the
range of the theoretical result.

>>>>

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
  In this paper, we present a novel way of calculating ground state energies for
  a quantum simulation using a Random Walk Monte Carlo simulation. The random
  walk consists of a walker making steps in random directions, with each step
  having a probability of causing the walker to die and the random walk to end,
  with the probability determined by a function of position. The function can be
  chosen to model specific quantum systems. The rate of death of the walkers is
  used to calculate the ground state energy. This paper explores the efficacy of
  such a method in reproducing the known ground state energy of an infinite
  square well, and the extensibility of the method to more complex
  systems. Using the infinite square well example, the simulation found the
  energy proportionality to be $1.2339 \pm 0.0008$, which is consister to high
  precision with the known $\frac{pi^2}{8}$ theoretical constant. Thus, we found
  that this method is very good at reproducing the known results to a high
  precision, and with good reliability, having very small variance in
  repeats. The method is extensible to higher dimensions, with a linear increase
  in time-complexity for each added dimension.
\end{abstract}

\section{Introduction}
\IEEEPARstart{T}{he} developments in computer power in recent years have opened
up the possibility for novel computational solutions to many problems that were
otherwise limited. We now have access to computers that can numerically solve
problems and run simulations that were previously too computationally intensive
to do.  One such problem is the calculation of the ground state energies of
different quantum systems. Many methods exist for solving these problems, using
both classical and quantum computational approaches. Whilst generally it may be
true that Quantum computating approahes are more suited to solving such problems
\cite{Mazzola}, these approaches are still in infancy and are not readily
accessible. Thus, there exist an abundance of classical computing approaches,
such as the Variational-Relaxiation algorithm \cite{Schroeder2017}. This is a
particularly useful algorithm for two-dimensional systems with non-separable
potentials but quickly becomes difficult to implement for more complex systems.

In this investigation, we explore an alternative Monte Carlo method using Random
Walk simulations, and demonstrate its efficacy with simple systems. This
approach has applications in many areas of Quantum Physics and is values due to
its effectiveness for more complicated systems.

@@

Random walks descibe motion as a series of steps in some vector space, with the
direction of each step being random, i.e. with there being an assigned likelihood
of a step in each possible direction. Consider a simple 1-dimensional line and a
walker standing at a point labelled the origin. The walker takes 20 steps, the
direction of each step (forwards or backwards on the line) is random. The
position of the walker at each step is shown in Figure \ref{fig:cartoon}.

\begin{figure}[H]%[!ht]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{images/cartoon.pdf}
    \caption{The position of a walker at each step in a 20-step random walk
      simulation. The average position of the walker does not necessarily remain
      at the origin as one might expect. Instead it is normal for the
      walker to finish the walk at some distance from the origin, as shown here.}
    \label{fig:cartoon}
  \end{center}
\end{figure}

@@

In this example, the walker had an equal likelihood of stepping forward or
backwards, but we can add a bias in a direction if we want to model a particular
phenomenon. The walk is also easily extensible to multiple dimensions, as for
each extra dimension, one extra random number must be drawn. This gives a linear
increase in time-complexity, which is convenient for more complex systems.

@@

Let us define $p(j,n+1)$ as the probability that the walker will be at position
$j$ after $n+1$ steps and $a(j)$ as the probability that the walker will die at
position $j$. Thus, for this to be the case, the walker would have had position
$j\pm1$ after $n$ steps. Thus, we can say:

@@

If $a(j)$ is small and $n$ is large, we can use Taylor's expansion to expand
each term in this expression and obtain a differential equation. If we then
make an ansatz substitution:

\begin{equation}
  p(j,n) = q(j) \exp(-\lambda n)
  \label{eq:firsteq}
\end{equation}
where $q(j)$ is an arbitrary function and $\lambda$ is the rate of death, the
differential equation in $p(j,n)$ simplifies to:

@@

\begin{equation}
  \label{eq:squarewell}
    a(j) =
    \begin{cases}
      0,& \text{if } j < J\\
      \infty,& \text{if } j \geq J
    \end{cases}
    \nonumber
\end{equation}
where J is a well-defined boundary. So the walker cannot die inside the well but
wil immediately die when they step outside, which we expect will mostly
happen given sufficient time. Inside the well, the potential is simply that of a
free particle \cite{Bransden2003}:

\begin{equation}
  \frac{-\hbar^2}{2m}\frac{d^2 \psi}{dj^2} = E\psi(j)
  \nonumber
\end{equation}
where $x$ is the position of the walker. By making the substitution
$x=J\frac{j}{R}$, such that $j=R$ corresponds to the walker being at the
boundary, we find:

@@

\begin{equation}
  E = \lambda R^2 \frac{\hbar^2}{mJ^2}
  \label{eq:kasia}
\end{equation}
where only $\lambda$ is an unknown quantity. Thus, by calculating rate of death
$\lambda$, we can calculate the ground state energy of the infinite square
well. The known ground state energy of an infnite square well is
$\frac{\pi^2}{8}\frac{\hbar^2}{mJ^2}$ \cite{Davies1998}, so we expect to find $\lambda
R^2$ close to $\frac{\pi^2}{8}$.

@@

We then considered the probability that a walker will survive $n$ steps, and use
the relationship between the number of walkers surviving $n$ steps and $n$ to
determine the rate of death $\lambda$, as shown in Equation \ref{eq:straightline}.

One method of reducing the computing time of the simulation is to introduce a
maximum number of steps. The walker will die if they reach the boundary of the
well, or if they reach this maximum number of steps, whichever happens
first. The effect of this method on the result is investigated in this paper.

% However, this will introduce some systematic error into the simulation,
% as there will be a disproportionately high number of walkers dying on the
% maximum number of steps. We also investigated these effects here.

% We expect to see an effect on the accuracy of our final ground state depending
% on the size of the infinite well. We investigate these effects by comparing the
% calculated ground state energy to the theoretical energy for different sized wells.

@@

\begin{figure*}[ht!]
  \centering
  \subfloat[Linear Scale]
  {\includegraphics[width=0.5\textwidth]{images/cum_exp_plot.pdf}
  \label{fig:cumhist}}
  \centering
  \subfloat[Log Scale]
  {\includegraphics[width=0.5\textwidth]{images/cum_line_plot.pdf}
  \label{fig:cumloghist}}
  \caption{Histograms showing the Probability of surviving to at least a
    particular step in an infinite square well with $J = 20$. The peak of 1 does
    not start at the origin but at step 100. This is because these steps were
    neglected in the plot as prior to this step the exponential shape is less
    clear. An exponential decay curve provides a good fit, with an $R^2$ value
    of 0.9999998. Plotting on a logarithmic scale shows the straight line fit,
    the gradient of which is $\lambda$, giving $\lambda J^2 = 1.2334$, with a
    negligible error. The fluctuation in the higher step number regions is due
    to the large variance in the small number of walkers that die at these
    steps.}
  \label{fig:cumplots}
\end{figure*}

% The simulation was first run for an infinite square well with boundary $J=20$
% with 1000000 walkers. The number of walkers surviving at each step was recorded
% and the histograms in Figure \ref{fig:cumplots} were created. The probability
% that a walker will survive at a particular step is simply the 1 minus the
% normalised cumulative sum of walkers dying at each step. The curve has been
% fitted with an exponential function of the form in Equation
% \ref{eq:firsteq}.

We first investigated an infinite square well with boundary $J=20$ and 1000000
walkers. We found the energy constant to be $1.2339 \pm 0.0008$, calculated from
the probability distribution of survival at a particular step. The probability
that a walker will survive at a particular step is simply the 1 minus the
normalised cumulative sum of walkers dying at each step. Figure
\ref{fig:cumplots} presents this probability and confirms the Anstatz of the
exponential function. The curve has been fitted with an exponential function of
the form in Equation \ref{eq:firsteq}. The gradient of Figure
\ref{fig:cumloghist} allowed for calculation of death rate which from Equation
\ref{eq:kasia} gives the calculated energy.

Figure \ref{fig:cumplots} results in a very good fit, with an $R^2$ value of
0.9999998, indicating the data does not vary much from the curve of best
fit. This is likely due to the very large number of walkers used in this
experiment, as allowed by the performant C++ implementation.  We can see this
better in Figure \ref{fig:cumloghist}, which is the same exponential plot fitted
on a logarithmic scale. The closeness of the data to the line of best fit is
evident here. The error in the fitted parameters is negligible, as shown by the
$R^2$ value. The gradient of the fitted line is taken to be $\lambda$ and thus
allows us to calculate $\lambda J^2 = 1.2334$, compared to the theoretical value
of $\frac{\pi^2}{8} = 1.2337$, quoting both values to the precision at which
they vary. Since the numerical error in the fits is negligible, it cannot be
propagated into an error in the final answer. Thus, we get the error in the
final answer from repeated runs of the simulation and taking the standard
deviation of the many values.

@@

\begin{figure}%[!ht]
  \begin{center}
    \includegraphics[width=0.45\textwidth]{images/line_plot.pdf}
    \caption{The probability of dying on a particular step in an infnite square
      well with $J=20$ as in Figure \ref{fig:hist}, plotted on a logarithmic
      scale. As explained for Figure \ref{fig:hist}, the peak probability is on
      a step greater than $J$. This is clear in this plot. It is also evident
      that there is significantly more spread in the points at higher
      steps. This is due to there being significantly fewer walkers dying on
      these steps, so the relative differences are higher. This explains the
      fluctuations seen at higher steps in Figure \ref{fig:cumloghist}.}
    \label{fig:loghist}
  \end{center}
\end{figure}

We observe some fluctuation in the data in the higher steps in Figure
\ref{fig:cumloghist}. This is because there are so few walkers surviving to this
many steps that there is more significant variance in their relative numbers. We
can observe this in Figure \ref{fig:loghist}. At higher step numbers, the spread
is significantly larger due to the greater relative variance in the small number
of walkers surviving to this many steps. When this data is cumulatively summed
to calculate the probability of survival shown in Figure \ref{fig:cumloghist},
the spread is present as the fluctuations.

\begin{figure*}[ht!]
  \centering
  \subfloat[Probability of dying on a particlar step in Linear scale]
  {\includegraphics[width=0.5\textwidth]{images/exp_plot_cutoff.pdf}
  \label{fig:expcutoff}}
  \centering
  \subfloat[Probability of surviving to at least a particular step in a
  logarithmic scale]
  {\includegraphics[width=0.5\textwidth]{images/cum_line_plot_cutoff.pdf}
  \label{fig:cum_line_cutoff_plot}}
  \caption{Histograms showing the results of the simulation when a maximm number
  of steps is introduced. If a walker reaches this number of steps, they
  automatically die, regardless of position. This results in a
  disproportionately high number of walkers dying at this maximum number, 2000
  in this case, as shown by Figure \ref{fig:expcutoff}. Although this presents
  no fluctuation at higher number of steps, as shown in Figure
  \ref{fig:cum_line_cutoff_plot}, some systematic error is introduced
  through this method.}
  \label{fig:cutoffplots}
\end{figure*}

It is possible to remove this variance by introducing a cutoff number of steps,
i.e. a maximum number of steps at which the walker will automatically die,
regardless of whether they reached a boundary or not. Thus, there will not be
such high variance in the number of walkers surviving to high number of
steps. This is presented in Figure \ref{fig:cum_line_cutoff_plot}. While the
Figure \ref{fig:cum_line_cutoff_plot} fit is observed to be better, with a
higher $R^2$ value, some systematic error has been introduced since there will
now be a disproportionately high number of walkers dying at the cutoff step as
can be seen in Figure \ref{fig:expcutoff}. Thus, the final $\lambda J^2$ value
will be less accurate. On a faster computer, with more efficient code, it is
possible to forgo the step cutoff and allow the simulation to run until all the
walkers die. This may take much longer but will ensure there will not be such a
systematic error introduced. This is the method used in this investigation.

@@

It is also necessary to investigate how varying the boundary $J$ affects the
accuracy of the final answer. Figure \ref{fig:multi_line_plot} presents the
probability plot from Figure \ref{fig:cumloghist} for many different boundary
$J$ values. No step cutoff was introduced. The calculated $\lambda J^2$ value is
shown in the legend. The gradient evidently changes, since the expected highest
number of steps would increase as the boundary is larger, as there is more
space for the walker to move before reaching a boundary. As shown in the legend,
the calculated $\lambda J^2$ values get closer and closer to the
theoretical value as $J$ increases. This is due to the fact that as $J$
increases, there are more walkers surviving to larger number of steps. Thus, we
can say that using a larger value of $J$ will result in a more accurate answer
but will also be more computationally intensive and take longer. Thus, we make a
tradeoff between speed and accuracy and choose $J=20$ for the final
investigation.

@@

In this investigation we demonstrated a method of calculating ground state
energies of a quantum system using Random walk computational simulations. The
investigation focussed on a one dimensional infinite square well, but can easily
be extended to more complex systems such as a cirular well in two dimensions.

The investigation explored the effects of varying the size of the well in
determining the ground state energy of a quantum system, and showed that this
Monte Carlo method produces more accurate results for ground state energies of
larger wells.  This is because for wells with larger boundaries, the walker can
take a larger number of steps on average before dying, and thus can populate
larger step bins. Thus, this method produces data that is close to the
theoretical result for larger infinite square wells.

The numerical result found the ground state energy proportionality constant to
be $\lambda J^2 = 1.2339 \pm 0.0008$, which is consistent with the known
theoretical value of $\frac{\pi^2}{8}$.
